SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-06-06 scipy-1.0/paper.tex

A problem faced by many open source projects is attracting and retaining developers.  While it is normal for some individuals to contribute to a project for a while and then move on, too much turnover can result in the loss of institutional memory, leading to mistakes of the past being repeated, APIs of new code becoming inconsistent with the old code, and a drifting project scope.
We are fortunate that the SciPy project continues to attract enthusiastic and competent new developers while maintaining the involvement of a small but dedicated ``old guard''. Pauli Virtanen, our BDFL, has been with the project for more than 10 years, and is still actively contributing code.  While the person acting as the release manager might change from one release to the next, Ralf Gommers acts as a general manager, keeping the release process moving smoothly and ensuring that pull requests get reviewed and merged where appropriate. Ralf is approaching his tenth year anniversary on the SciPy project and shows no signs of slowing down. There are early contributors, such as Robert Kern and St\'{e}fan van der Walt, who contributed much to SciPy over the last 10 or more years and while not currently writing code for SciPy, still contribute to discussions of bug reports and reviews of new code contributions. There are an additional half dozen or so currently active developers who have been contributing steadily for five or more years. The combination of a committed old guard and a host of new contributors ensures that SciPy will continue to grow while maintaining a high level of quality.

>>>>

A problem faced by many open source projects is attracting and retaining developers. While it is normal for some individuals to contribute to a project for a while and then move on, too much turnover can result in the loss of institutional memory, leading to mistakes of the past being repeated, APIs of new code becoming inconsistent with the old code, and a drifting project scope.
We are fortunate that the SciPy project continues to attract enthusiastic and competent new developers while maintaining the involvement of a small but dedicated ``old guard''. There are contributors who were present in the early years of the project who still contribute to discussions of bug reports and reviews of new code contributions. Our BDFL has been with the project for more than 10 years and is still actively contributing code, and the head of our Steering Council, who also acts as a general manager, is approaching his eleventh anniversary. An additional half dozen or so active developers have been contributing steadily for five or more years. The combination of a committed old guard and a host of new contributors ensures that SciPy will continue to grow while maintaining a high level of quality.
